\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-01-08 thesis_template/paper0904.tex
adding citations in bibtex

\lhead{Type 1 Diabetes Review} %This needs to change
\rhead{Bianca Flaim, Oluwalonimi Ayekun, and Alexander Turco}
\title{\sc Examining the Molecular Basis of Type 1 Diabetes}
\author{\sc Bianca Flaim, Oluwalonimi Ayekun, and Alexander Turco}

@@

@@

\subsection{What is Type 1 Diabetes?}
Over the last 70 years, developed countries around the world have seen a steady increase in the incidence of type 1
diabetes (T1D) (Patterson et al. 2012; Todd 2010). It is generally thought that T1D is due to the immune-mediated destruction of
pancreatic $\beta$-cells which are responsible for the production of insulin (Atkinson, G S Eisenbarth, and Michels 2014; Todd 2010).
Autoantibodies specifically targeting $\beta$-cells, as well as macrophage and lymphocyte infiltration of the pancreas are responsible
for the destruction of insulin-producing $\beta$-cells (Van den Driessche et al. 2009). These $\beta$-cells are found within the islets of Langerhans and they have the ability to sense glucose and subsequently release insulin to maintain healthy blood-glucose levels (Bluestone, Herold, and G Eisenbarth 2010). Although it is known to be a common chronic disease in children, diagnosis of
T1D can occur at any age (Atkinson, G S Eisenbarth, and Michels 2014). Symptoms associated with disease onset, especially in
children and adolescents, are typically polydispia (extreme thirst), polyphagia (extreme hunger), polyuria (excessive urination),
and hyperglycaemia (high blood sugar) (Atkinson, G S Eisenbarth, and Michels 2014). Research surrounding T1D tends to
revolve around the search for environmental triggers, as well as genetic factors which contribute to the disease (Todd 2010).
Rapid advancements in both molecular biology and genetic sequencing methods have contributed to an increase in papers which
examine the genetic basis of the disease. It is believed that the nature component (genetic factors, molecules, cells) of T1D will
provide insight into disease mechanisms, and at the same time help researchers to identify environmental factors which play a
role in the development of the disease (Todd 2010).

\subsection{Insulin Hormone Production and Release}
The insulin hormone is a peptide hormone encoded on INS gene, found on chromosome 11 (cluster p15.5) (Ohneda,
Ee, and German 2000; Tokarz, MacDonald, and Klip 2018). Gene expression is regulated by several enhancer elements found
upstream of the INS gene, including IDX1, MafA, NeuroD1 (Tokarz, MacDonald, and Klip 2018). As insulin is a key hormone
involved in the feedback loop to establish blood glucose homeostasis, glucose levels also influence insulin production (Ohneda,
Ee, and German 2000; Vranic, Hollenberg, and Steiner 1985). Transcription from the INS gene yields a preproinsulin mRNA
molecule, which exits the $\beta$-cell’s nucleus and is translated by ribosomes situated within the rough endoplasmic reticulum
(RER) to produce a preproinsulin polypeptide (Tokarz, MacDonald, and Klip 2018). After translation, a series of posttrans-
lational modifications are required, beginning with removal of the signal sequence within the RER (Tokarz, MacDonald, and
Klip 2018). Signal removal allows polypeptide (now proinsulin) trafficking to the trans-Golgi network, where the C-peptide
is proteolytically cleaved by the prohormone convertases PC1/3 and PC2 (Klimek et al. 2009; Tokarz, MacDonald, and Klip
2018). Proinsulin is then appropriately folded and stabilized through the formation of disulfide bonds, yielding a mature insulin
protein (Mathieu, Gillard, and Benhalima 2017; Tokarz, MacDonald, and Klip 2018). Insulin is then packaged into granules
and trafficked along the cell’s actin microtubule network where they are stored within the $\beta$-cell’s plasma membrane, prepared
for secretion once the cell receives the appropriate signal to release insulin (Tokarz, MacDonald, and Klip 2018).

Glucose entry in the $\beta$-cell triggers a cascade of intracellular events which terminates in insulin release. Once blood glu-
cose rises typically above 100 mg/dL, glucose begins to enter the $\beta$-cell’s cytoplasm via membrane GLUT1 channels (Tokarz,
MacDonald, and Klip 2018; Vranic, Hollenberg, and Steiner 1985). Glucokinase then phosphorylates the glucose, trapping it
within the cell and beginning the process of glycolysis, resulting in the production of adenosine triphosphate (ATP) and pyru-
vate (Tokarz, MacDonald, and Klip 2018). Pyruvate then undergoes subsequent metabolic steps, including entering the Krebs
cycle and the electron transport chain within the mitochondria, resulting in the production of lots of ATP. Within the cytoplasm,
the increased ATP/adenosine diphosphate (ADP) ratio is detected, resulting in the closure of ATP-sensitive K+ ion channels
(Tokarz, MacDonald, and Klip 2018). Since the potassium ions ca no longer flow out of the cell, the closure of these channels
results in a more positive membrane potential, leading to depolarization of the cell once the membrane potential reaches –50
millivolts (mV) (Tokarz, MacDonald, and Klip 2018). Depolarization of the cell activates voltage-dependent Na+ and Ca2+
channels, allowing the influx of sodium and calcium ions, further increasing membrane potential (Tokarz, MacDonald, and Klip
2018). The influx of calcium ions triggers SNARE proteins, Munc18, and syntaxin proteins to initiate insulin vesicle fusion and
release into the bloodstream (Tokarz, MacDonald, and Klip 2018). As insulin is released and plasma glucose levels begin to
drop, the signal is terminated as the SERCA pump removes calcium ions from the $\beta$-cell’s cytoplasm (Tokarz, MacDonald, and
Klip 2018). Additionally, the signal is terminated as granule exocytosis requires ATP hydrolysis, thus reducing the cytosolic
ATP:ADP ratio, and triggering the reopening of ATP-sensitive K+ channels (Tokarz, MacDonald, and Klip 2018). Allowing
potassium ions to flow out of the cell reduces the membrane potential, resulting in the closure of voltage-gated Na+ and Ca2+
channels. The process of insulin release has been described as a biphasic process, with an initial burst as the cell initially depo-
larizes and releases all primed insulin granules within the cell membrane, and a second, prolonged phase as the cell’s network
reorganizes itself to recruit more insulin granules to the plasma membrane for subsequent exocytosis (Tokarz, MacDonald,
and Klip 2018). Within an islet of Langerhans, which contains many $\beta$-cells, which are connected by gap junctions, allowing
rapid paracellular cell-to-cell communication, and resulting in a large, rapid, release of insulin from the pancreas when needed
(In’t Veld and Marichal 2010; Tokarz, MacDonald, and Klip 2018).

\subsection{Insulin-Insulin Receptor Binding Mediated Glucose Storage and Uptake}
Insulin binds to the insulin receptor (IR) expressed on the cell membrane of its target cells. The IR is a disulphide-linked
receptor tyrosine kinase homodimer comprised of two $\alpha$-subunits and two $\beta$-subunits. After insulin binding, the IR undergoes a conformational change bringing the two IR monomers closer and allowing for autophosphorylation (De Meyts 2016). During
autophosphorylation, each IR monomer adds a phosphate group to the $\beta$-unit of the other IR monomer resulting in the activation
of the IR receptor. Once activated, the IR becomes capable of activating and binding to the adaptor protein insulin-receptor
substrate 1 (IRS-1). IRS-1 acts as a docking site for proteins with Src-homology-2 domains, such as the p85 subunit of PI
(3)K which helps facilitate the recruitment PI (3)K to the plasma membrane (Lizcano and Alessi 2002; Sun et al. 1991). Upon
being recruited to the plasma membrane, PI (3)K catalyzes the conversion of phosphatidylinositol (4,5)-biphosphate (PI (4,5)
P2) into phosphatidylinositol (3,4,5) triphosphate (PI (3,4,5) P3). PI (3,4,5) P3 can phosphorylate the AKT (also known as
protein kinase B) (Sun et al. 1991). The increased concentration of PI (3,4,5) P3 molecules along the cell membrane facilitates
the recruitment of AKT to the plasma membrane. Once at the plasma membrane, AKT is phosphorylated by two other protein
kinases, PDK1 at residue Thre308 and MTORC at residue Ser473. The phosphorylation of the protein at these two residues
allows for its activation (Leto and Saltiel 2012; Menting et al. 2013). Upon its activation, AKT dissociates from the membrane
and begins to interact with number of different effector proteins within the cytosol and nucleus, including GSK3 (Lizcano and
Alessi 2002). GSK3 is a serine/threonine protein kinase that can inhibit the activity of glycogen synthase, a key enzyme in the
process of glycogenesis. When AKT phosphorylates GSK3 it inhibits the activity of this kinase, therefore increasing glycogen
synthase and the rate of glucose-to-glycogen conversion. This is how insulin increases glucose storage inside of muscle and fat
cells.

In addition to glucose storage, insulin also helps facilitate the process of GLUT-4 translocation to the cell membrane
in muscle and adipose (fat) cells. GLUT-4 is one of the several GLUT proteins responsible for transporting glucose across
the blood vessel into cells in the human body (Li et al. 2019). When insulin is not bound to the IR, about 80% of GLUT-4
remains sequestered in specialized, intracellular organelles known as GLUT-4 storage vesicles (GSVs) while the other 20%
cycle slowly between the GSVs and plasma membrane (Fazakerley, Koumanov, and Holman 2022). Within 5-10 minutes of
insulin-mediated intracellular signalling, the number of GLUT-4 receptors expressed along the surface of adipose and fat cells
increases by over 50% (Fazakerley, Koumanov, and Holman 2022; Stöckli, Fazakerley, and James 2011). Insulin increases
the amount of GLUT-4 at the plasma membrane primarily by promoting the fusion of GSVs with the plasma membrane (also
known as GSVs exocytosis) (Leto and Saltiel 2012). Like with glucose storage, AKT acts as a central mediator of this process
through its intracellular interactions with several important molecules and proteins involved in GSVs exocytosis. For instance,
AKT is capable of phosphorylating both RAB-GAP AS160 (also referred to asTBC1D4) and the RAL-GAP complex, each of
which have important roles in GLUT-4 vesicle trafficking and targeting to the plasma membrane (De Meyts 2016; Leto and
Saltiel 2012). Along with RAB-GAP AS160 and the RAL-GAP complex, AKT has also been shown to interact with SNARE
regulatory proteins, SYNIP and CDP138, which are necessary for the fusion of GSVs to the plasma membrane.

In addition to the PI (3)K-AKT pathway, however, insulin is also capable of promoting GLUT-4 translocation via another
intracellular signalling pathway. This pathway is mediated by the adaptor protein APS, which binds with high affinity to
the insulin-receptor (Yu et al. 2007). After APS is phosphorylated by the IR, it recruits a complex consisting of the proto-
oncogene c-CBL and the-CBL associated protein (CAP) facilitating the IR-catalyzed Tyr phosphorylation of c-CBL. Following
phosphorylation by the IR, c-CBL becomes capable of interacting with the adaptor protein CRK which is bound to the GEF
(Guanine-Exchange-Factor) C3G. This interaction allows C3G to initiate the activation of TC10, an RHO-family GTP-Ase,
localized in the lipid rafts of the plasma membrane (Leto and Saltiel 2012). TC10 is then able to interact with its’ effector
protein called PIST 1, which then binds to and directs the cleavage of the protein TUG. In basal conditions (under low insulin
concentration), TUG binds to GLUT-4 in GSVs preventing the trafficking of these GSVs, and thus GLUT-4 translocation, to the
plasma membrane. Insulin-induced cleavage of the TUG protein stimulates the dissociation of protein from GLUT-4 enabling
the trafficking of GSVs to the plasma membrane (Li et al. 2019; Yu et al. 2007). In the absence of this step, GSVs regulated
trafficking and GLUT-4 translocation is inhibited in adipocyte cells (Chang, Chiang, and Saltiel 2004). In addition to facilitating
the cleavage of TUG, TC10 also interacts with the protein EXO70 which belongs to the exocyst complex and is involved in the
docking of secretory vesicles to the plasma membrane.

\subsection{Type 1 Diabetes Symptom Pathophysiology and Possible Complications}
T1D is said to proceed in 3 phases – two presymptomatic phases, followed by a symptomatic phase that increases in
severity as the disease progresses (Katsarou et al. 2017; Norris, Johnson, and Stene 2020). The first phase is characterized
by initial immune infiltration of the pancreas by macrophages, dendritic cells, CD8+ and CD4+ T-cells, and autoantibodies
specific against $\beta$-cells, resulting in the rapid loss of functional $\beta$-cells (Katsarou et al. 2017). This stage is followed by the initial development of hyperglycemia, which may present as asymptomatic at first as the pancreas retains some functionality (Katsarou et al. 2017). As immune destruction continues, $\beta$-cell functionality dramatically decreases, resulting in more severe hyperglycemia and the development of symptoms (Katsarou et al. 2017). Primary symptoms include polyuria, polydipsia, and polyphagia (R A Guthrie and D W Guthrie 2004). As glucose accumulates within the bloodstream, the kidneys attempt to
rectify the imbalance by excreting more glucose in the urine (R A Guthrie and D W Guthrie 2004). As the nephron excretes
glucose into the urine, water follows from the bloodstream into the urine, resulting in a greater volume of urine and the primary
symptom of polyuria (R A Guthrie and D W Guthrie 2004). Increased urination in attempts to reduce blood glucose results
in dehydration, so this causes the polydipsia as the body’s mechanism to increase water intake and restore hydration and
water homeostasis (R A Guthrie and D W Guthrie 2004). The final primary symptom, polyphagia, is increased hunger due to
reduced fuel available to cells (R A Guthrie and D W Guthrie 2004). Primary complications include nephropathy, neuropathy,
retinopathy, risk of cardiovascular disease and peripheral artery disease, and risk of cerebrovascular disease (Katsarou et al.
2017; McGill and Levitsky 2016; Melendez-Ramirez, Richards, and Cefalu 2010; Wherrett et al. 2018). These conditions
are largely related to the severity and length of hyperglycemic exposure, especially due to the increased stress on the kidneys
due to increased glucose excretion. As hyperglycemia exposure increases, this can increase the risk of albuminuria, which
may progress to complete nephropathy (Melendez-Ramirez, Richards, and Cefalu 2010). Neuropathy may arise in the case of
hypoglycemia (in instances where too much insulin is injected), as the brain primarily relies on glucose as its fuel source, and
reduced glucose delivery to the brain may result in neuronal death and possible cognitive impairments and deficits (Katsarou
et al. 2017). Hyperglycemia is also linked to the production of microaneurysms in blood vessels feeding the retina, leading
to possible retinopathy and fluid leakage resulting in macular edema (Melendez-Ramirez, Richards, and Cefalu 2010). Lastly,
hyperglycemia can trigger a severe complication known as diabetic ketoacidosis (DKA). Hyperglycemia causes the production
of ketones as an alternate source of fuel when insulin is critically low, and cells cannot access glucose (Cashen and Petersen
2019). In this case, ketogenesis begins, and can result in the acidification of the blood, and can also result in cerebral edema
and hypokalemia which can become fatal in severe cases (Cashen and Petersen 2019).

\subsection{Mutations associated with Type 1 Diabetes}
T1D is a complex disease, meaning it can be influenced by a variety of environmental and genetic risk factors (Brorsson
et al. 2010). The concordance of T1D among monozygotic and dizygotic twins, as well as numerous studies that have identified
genes associated with T1D, provide good evidence for a strong genetic determinant of disease (Erlich et al. 2008). For over
thirty years, it has been known that the human leukocyte antigen (HLA) region on chromosome 6 contributes to the risk of
developing T1D (Brorsson et al. 2010). The HLA region contains genes which code for proteins that have immune function,
particularly in the regulation of the immune response (Choo 2007). More specifically, it has been found that certain alleles at
the HLA-DRB1, HLA-DQA1, and HLA-DQB1 loci are more strongly associated with T1D than others (Erlich et al. 2008).
Although studies have identified these specific alleles, the consensus remains that more work must be done to further identify
causative variants and their DNA profile (Brorsson et al. 2010). The complexity of T1D makes it extremely difficult to narrow
down the cause to one single gene, but there are a very small number of diabetes cases which do in fact result from single
gene mutations (Yang and Chan 2016). Two major forms of monogenic diabetes are Neonatal diabetes mellitus (NDM) and
maturity-onset diabetes of the young (MODY) (Yang and Chan 2016). These monogenic forms of diabetes are typically the
result of mutations in genes which code for proteins that reduce $\beta$-cell function (Steck and Winter 2011). It is interesting to
note that the single gene mutations found to cause NDM and MODY, have also been found to be associated with T1D (Yang
and Chan 2016). Two examples of monogenic diabetes genes which have also been found to be associated with T1D are the
preproinsulin gene (INS), and the Gli-similar 3 gene (GLIS3) (Yang and Chan 2016). The GLIS3 gene codes for a transcription
factor which regulates islet development and insulin gene transcription, and the INS gene encodes the peptide hormone insulin
(Steck and Winter 2011; Yang and Chan 2016). Single nucleotide polymorphisms (SNPs) are typically what affect the normal
function of both genes, but it has also been found that allelic variants of the genes lead to both monogenic diabetes and T1D
(Yang and Chan 2016).

\subsection{Type 1 Diabetes Treatments and Health Considerations}
As the $\beta$-cell functionality is destroyed due to immune destruction, functionality cannot be restored. Thus, the standard
of care involves continuous glucose monitoring and regulation of blood sugar levels via insulin injections (McGill and Levitsky
2016). Many patients opt for insulin pumps, otherwise known as a closed-loop pancreas system (Wherrett et al. 2018). This
system is an artificial system that features an insulin pump, and a glucose sensor which can detect when insulin should be
secreted. Some of these systems may infuse just insulin, others also feature a glucagon pump to increase blood sugar in case
too much insulin was secreted (Wherrett et al. 2018). Alternatively, patients may opt for standard insulin injections. A key
component of T1D treatment is patient education on their condition and the body’s natural fluctuations of blood sugar levels
throughout the day. For example, it is important for patients to understand that prolonged fasting, illness, or intense exercise can
reduce blood sugar levels and naturally cause a hypoglycemic crisis (McGill and Levitsky 2016). In the event of hypoglycemia,
it is important to detect as soon as possible and consume a small amount of sugar (15 grams typically recommended, available
in juice, candies, or glucose gels) (Katsarou et al. 2017). Lifestyle changes such as eating snacks prior to bedtime and exercising
earlier in the day can be beneficial in preventing nocturnal hypoglycemia (McGill and Levitsky 2016). Due to the number of
potential complications which may arise from T1D, physicians should also monitor patients for other comorbidities including
other autoimmune conditions, kidney failure, dyslipidemia, retinopathy, and other hormonal disease (Katsarou et al. 2017).
Further, patients are encouraged to consult dieticians to develop healthy meal plans to regulate blood sugar levels and join
community support groups (Katsarou et al. 2017). T1D patients are at increased risk of mental health issues such as anxiety,
depression, and eating disorders due to the perceived lack of autonomy and increased stress load due to their disease (Katsarou
et al. 2017).

>>>>

\lhead{Cells at War: Game-Based Learning} %This needs to change
\rhead{Bianca Flaim, Alexander Turco}
\title{\sc Cells at War: The Playfulness of Game-Based Learning}
\author{\sc Bianca Flaim, Alexander Turco and Rosa da Silva}

@@

\section{Abstract}

\newpage

@@

\subsection{Introduction - Maybe move to Abstract, it encompasses everything}
After many years of trying to adapt to educational innovations of the 21st Century, educators will soon be looking into the not too distant future and considering what modern learning in post-secondary education will look like in the 22nd Century. Technological advances will continue to transform the landscape of the classroom and the use of digital games, although a source of controversy and debate, will prove to be highly effective instructional tools that can promote problem solving skills and critical thinking. Their use has already started to change the structure of the class in the elementary classroom as they serve to energize and engage students in their learning and improve learning, creativity and imagination. The traditional construct of the classroom has started to evolve, embracing a new way in which knowledge, skills and attitudes can be acquired. Cells at War is a collection of scientific video games developed through interdisciplinary efforts that reinforces the notion that video games are highly effective tools used to enhance instructional methods. (Not only enhancing but teaching and engaging, ask rosa). – I don’t know if I should mention the game but I like this line.

\subsection{Children and Play}

Although technological ecosystems have been established in schools for some time, its landscape continues to be missing significant components to create a fully functioning ecosystem. One of these key components is that educators are reticent to embrace digital technology and gaming as the new norm in the classroom. Kindergarten classrooms in Ontario are bustling places of activity, reflective of active inquiry through play. Exploration and provocations drive their curiosity while simultaneously developing their oral language and critical thinking skills \citep{kindergartencurriculum}. Digital games on ipads are being used to develop literacy and numeracy skills. Some educators however, oppose the use of digitized games especially in higher education and have not fully embraced the notion that learning can actually take place through play. We believe that play is paramount for children in their formative years and educational theorists like Vygotsky affirm this. He was firm in his belief that play is the leading line of development during preschool years \citep{vygotsky1967play}. Unfortunately, in many classrooms, educators continue to feel more comfortable in engaging in antiquated and traditional methods of instruction that consist of a didactic approach to learning. The need to challenge current educational practices is paramount as educators are currently teaching students from the perspective of their own past rather than the realities of the students’ future. – I like this line, its powerful that’s why I highlighted it.

\subsection{What Happens to Play Beyond the Formative Years?}

The need to engage and motivate learners does not cease to be a need in a student’s educational career. However, what does become a priority in higher academic years are measurable student outcomes \citep{ball2012politics,shore2010beyond,leather2021pedagogy}. Tests and quizzes take precedence over the formative process of learning. Assessment of learning (tests and quizzes) dominates an educator’s instructional practices which in turn diminishes the value of the experiential learning process (assessment as learning). Assessment methods seem to be based on antiquated teaching practices, which have been influenced by our Victorian educational heritage that is rooted in a persistent view of fear of play \citep{wood2013play}. This rigidity in instructional norms appears to have taken hold in our classrooms which diminishes the value and importance of games in the classroom. \citet{reich2020failure} argues that schools are complex and conservative institutions that have little incentive to adopt or test novel approaches.

It can be argued that this fear of play is also due in large part to limited resources and training being provided to educators. Teachers require technological and pedagogical supports to develop their understanding of game based learning in the classroom. The expectation therefore to incorporate new and innovative teaching methodologies in the classroom is unrealistic without providing teachers with the appropriate training needed to do so. Incorporating game based learning in teacher practice is impacted by a lack of professional development opportunities that can systematically guide them in using games for teaching, learning, and assessment \citep{fishman2014empowering,ruggiero2013video,foster2020principles}. Might want to add a line here, don’t wanna end on quote

\subsection{Do Games Help or Hurt Learning: The Debate Over Game-Based Learning}

The debate of whether game based learning helps or hinders learning is ongoing. What comes into question in opposition to game based learning is that it serves to act as a source of entertainment and amusement rather than for educative purposes. Many individuals associate play with children, and therefore believe that play is trivial and unimportant (Play and learning Prensky). In fact, one does not learn to play, but rather plays to learn. Play is where a spark is ignited and the source in which curiosity is peaked. It is not silly, trivial or irrelevant but has a biological and evolutionary function which has a strong connection to learning (Play and Learning Presnky). It is, as Danny Hillis, founder of Thinking Machines and a former Disney Fellow has stated something every single culture does (play and learning Prensky).

Arguing the merits behind the development and creation of digital games for use in post-secondary classrooms can appear effortless. However, what cannot be overlooked at times is that educators spend a great deal of time planning and executing engaging lessons which can become time consuming and onerous. Svinicky and McKeachie (2013) argue that the biggest barrier to the use of games therefore is logistic. Although games can be fun and engaging, we know that our classrooms today are comprised of diverse students with varying needs and a one size fits all approach does not work.

\subsection{The Benefits of Using Video Games at the Post-secondary Level}

Classrooms are becoming a place where the student is now involved in the learning process. Rules, goals and objectives, outcomes, competition, interaction, and story are what Mark Prensky refers to as the six key structural elements of games (Prensky digital game based learning). These powerful factors are what set games apart from other engaging activities. Traditional forms of educational media lack what video games provide, a high degree of interactivity (coller, scott, mechanical engineering paper). Video games challenge individuals to work within specific parameters and respond to situations that occur in the game (coller, scott, mechanical engineering). The way in which individuals respond to challenges presented in video games allows them to think critically, strategize, and work collaboratively in an interactive and engaging manner.

Video games are visually appealing, stimulating, and heighten our senses in many ways. We become addicted to the hormone boost our brains receive when we achieve results (Lubomir Tomaska). They allow us to learn through doing and creating (video games and education Kurt Squire). Like play, upon beginning a video game, one is completely immersed into a whole new world without boundaries (coller, scott, engineering). Each player is engaged in a creative process where they are free to discover the limitless possibilities contained within the game. In a school setting, we are often taught there is one solution or right answer or way of doing something. Video games challenge this by giving players multiple entry points and pathways to consider.

The growing evidence of the effectiveness of video games in the classroom is emerging, and the value of game based learning is evident throughout various disciplines. In 2005, Northern Illinois University began teaching an undergraduate course in Numerical Methods using a video game called “NIU-Torcs” (Coller, Scott). Students were observed spending twice the average amount of time on coursework than other subject areas (Coller, Scott). Other games are being developed for nursing education which focus on developing medication calculation skills. This is an area of global concern perhaps due to test anxiety and low mathematical self-efficacy in nursing students (Foss, Mordt Medication calculation).  Game based learning not only provides students with infinite possibilities for discovery but sustains student interest, builds confidence, and helps to improve cognition and learning outcomes.

\subsection{Concluding the Lit Review - I dont know if I wanna put this here}

The long-term positive effects of Game-Based Learning will continue to be researched and studied. Although empirical evidence is slowly emerging but still limited, studies and research to date are proving that Game-Based Learning has the potential to transform post secondary classrooms. They are moving from teacher centred to student centred learning hubs which serve to create a learning environment in which students are able to take risks, explore, discover, fail and try again.
